Neutral models of \textit{de novo} gene emergence suggest that gene evolution has a preferred trajectory

### 2022-12-22 Manuscripts/deNovoRates2.tex
modified:   Manuscripts/deNovoRates2.tex

\begin{align}
P_\textit{RNA-gain}(k) &  = (P_\textit{TATA-stay} + P_\textit{Inr-stay})\times P_\textit{polyA-gain}\times (P_\textit{nopolyA-stay})^{3k-5} \nonumber\\[1ex]
%
& + (P_\textit{TATA-gain} + P_\textit{Inr-gain})\times P_\textit{polyA-stay}\times (P_\textit{nopolyA-stay})^{3k-5} \nonumber \\[1ex]
& + (P_\textit{TATA-stay} + P_\textit{Inr-stay})\times P_\textit{polyA-stay}\times (P_\textit{nopolyA-stay})^{3k-5} \times (3k-6) \times P_\textit{polyA-loss}
\label{eqrnagain}
\end{align}

>>>>

\begin{align}
P_\textit{RNA-gain}(k)  = & \ (P_\textit{TATA-stay} + P_\textit{Inr-stay})\times P_\textit{polyA-gain}\times (P_\textit{nopolyA-stay})^{3k-5} \nonumber\\[1ex]
%
& + (P_\textit{TATA-gain} + P_\textit{Inr-gain})\times P_\textit{polyA-stay}\times (P_\textit{nopolyA-stay})^{3k-5} \nonumber \\[1ex]
& + (P_\textit{TATA-stay} + P_\textit{Inr-stay})\times P_\textit{polyA-stay}\times (P_\textit{nopolyA-stay})^{3k-5} \times (3k-6) \times P_\textit{polyA-loss}
\label{eqrnagain}
\end{align}
